Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-21 report/report.tex
Mention van Oorts quality criteria

\section{Related work}
Fan et al, 2015
Kunze, 2012 (reference in Fan et al)
Haklay

@@

(Haklay 2010) specifices a comprehesive list of 8 accuracy classes when it comes to evaluating the quality of geographic information.

@@

>>>>

\section{Related work}
Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers. (van Oort, 2006)

Haklay

Fan et al, 2015
Kunze, 2012 (reference in Fan et al)

@@

(Haklay 2010) presents a comprehesive list of 8 accuracy classes when it comes to evaluating the quality of geographic information (van Oorts criteria)

@@

\bibitem{van-oort-06}
van Oort P A J. 2006. Spatial Data Quality: From Description to Application. PhD Thesis, Wageningen University.
